Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-03-11 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
cite Stan as aksed by the Stan team

The joint posterior parameter distributions are estimated by sampling using the dynamic HMC algorithm implemented in Stan \citep{carpenter2017stan,betancourt2017conceptual}. $\mathrm{Normal}(0,1)$, $\mathrm{Normal}(0,3)$ and $\mathrm{Gamma}(1.2,0.2)$ prior distributions has been used for the observation noise $\sigma$, covariance function marginal variance $\alpha$, and length-scale $\ell$, respectively. We use the same prior distributions to fit the exact GP model as the HSGP models.

@@

The joint posterior parameter distributions are estimated by sampling using the dynamic HMC algorithm implemented in Stan \citep{carpenter2017stan,betancourt2017conceptual}. $\mathrm{Normal}(0,1)$, $\mathrm{Normal}(0,10)$ and $\mathrm{Normal}(0,2)$ prior distributions has been used for the observation noise $\sigma$, covariance function marginal variances $\bm{\alpha}=\{\alpha_1 \alpha_2, \alpha_3\}$, and length-scales $\bm{\ell}=\{\ell, \ell,\ell\}$, respectively. A $\mathrm{Normal}(0,0.1)$ prior distribution has been used for the standard deviation $\tau$ of the Student's $t$ distribution with 1 degree of freedom used to model $f_4$ (i.e., the special days effects).

@@

The joint posterior parameter distributions are estimated by sampling using the dynamic HMC algorithm implemented in Stan \citep{carpenter2017stan,betancourt2017conceptual}. $\mathrm{Normal}(0,1)$, $\mathrm{Normal}(0,3)$ and $\mathrm{InverseGamma}(2,0.5)$ prior distributions has been used for the observation noise $\sigma$, covariance function marginal variance $\alpha$, and length-scales $\ell$, respectively. We use the same prior distributions to fit the exact GP model as the HSGP models on the synthetic data sets.

@@

Experiments have been conducted to empirically recognize time of computation of the HSGP model in multivariate cases and different number of sample data points. Dynamic HMC algorithm implemented in Stan \citep{carpenter2017stan,betancourt2017conceptual} was used for the experiments. Implementation and sampling has been done only for the sample data.

>>>>

The joint posterior parameter distributions are estimated by sampling using the dynamic HMC algorithm implemented in Stan \citep{StanTeam:2021}. $\mathrm{Normal}(0,1)$, $\mathrm{Normal}(0,3)$ and $\mathrm{Gamma}(1.2,0.2)$ prior distributions has been used for the observation noise $\sigma$, covariance function marginal variance $\alpha$, and length-scale $\ell$, respectively. We use the same prior distributions to fit the exact GP model as the HSGP models.

@@

The joint posterior parameter distributions are estimated by sampling using the dynamic HMC algorithm implemented in Stan \citep{StanTeam:2021}. $\mathrm{Normal}(0,1)$, $\mathrm{Normal}(0,10)$ and $\mathrm{Normal}(0,2)$ prior distributions has been used for the observation noise $\sigma$, covariance function marginal variances $\bm{\alpha}=\{\alpha_1 \alpha_2, \alpha_3\}$, and length-scales $\bm{\ell}=\{\ell, \ell,\ell\}$, respectively. A $\mathrm{Normal}(0,0.1)$ prior distribution has been used for the standard deviation $\tau$ of the Student's $t$ distribution with 1 degree of freedom used to model $f_4$ (i.e., the special days effects).

@@

The joint posterior parameter distributions are estimated by sampling using the dynamic HMC algorithm implemented in Stan \citep{StanTeam:2021}. $\mathrm{Normal}(0,1)$, $\mathrm{Normal}(0,3)$ and $\mathrm{InverseGamma}(2,0.5)$ prior distributions has been used for the observation noise $\sigma$, covariance function marginal variance $\alpha$, and length-scales $\ell$, respectively. We use the same prior distributions to fit the exact GP model as the HSGP models on the synthetic data sets.

@@

Experiments have been conducted to empirically recognize time of computation of the HSGP model in multivariate cases and different number of sample data points. Dynamic HMC algorithm implemented in Stan \citep{StanTeam:2021} was used for the experiments. Implementation and sampling has been done only for the sample data.
